Results

### 2025-02-26 notebooks/00_index.qmd
feat: combine density and temp

```{julia}
using Speasy
using Speasy: DataSet
spz = speasy()

@@

tvars_psp = [
    "cda/PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc",
    ["cda/PSP_SWP_SPI_SF00_L3_MOM/DENS", "cda/PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"],
    "cda/PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN",
    "cda/PSP_SWP_SPI_SF00_L3_MOM/TEMP",
]

tvars_wind = [
    "cda/WI_H2_MFI/BGSE",
    "cda/WI_PM_3DP/P_DENS",
    "cda/WI_PM_3DP/P_VELS",
    "cda/WI_PM_3DP/P_TEMP",
]

f = Figure()
add_title = true
tplot(f[1, 1], tvars_psp, tmin, tmax; add_title)
tplot(f[1, 2], tvars_wind, tmin, tmax; add_title)
add_labels!()
f
```

>>>>

```{julia}
using Speasy
speasy()

@@

density_tvar = SpaceTools.DataSet(
    "Density",
    [
        "cda/PSP_SWP_SPI_SF00_L3_MOM/DENS",
        "cda/PSP_FLD_L3_RFS_LFR_QTN/N_elec",
        "cda/PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"
    ]
)

# tvars_psp = [
#     "cda/PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc",
#     density_tvar,
#     "cda/PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN",
#     "cda/PSP_SWP_SPI_SF00_L3_MOM/TEMP",
# ]

tvars_wind = [
    "cda/WI_H2_MFI/BGSE",
    ["cda/WI_PM_3DP/P_DENS" "cda/WI_PM_3DP/P_TEMP"],
    "cda/WI_PM_3DP/P_VELS",
]

f = Figure()
add_title = true
# tplot(f[1, 1], tvars_psp, tmin, tmax; add_title)
tplot(f[1, 2], tvars_wind, tmin, tmax; add_title)
add_labels!()
f
```
